Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-14 manuscript/manuscript.tex
Minor modification in manuscript

Fig.~\ref{fig:exp-densities} shows the density functions for each value of $b$ and
Fig.~\ref{fig:delta-exponential} shows the resulting relative
differences ($V$ and $g_z$).
In order to improve the visualization of the results, each curve corresponds to the
maximum difference between all shell models for the same value of $b$.
The relative difference for $V$ and $g_z$ falls below the 0.1\% threshold
for each computation grid, shell model and $b$ value if $\delta = 0.1$.
These results also show that there is no significant relation between the $b$
value and the numerical error, proving that the density-based discretization algorithm
is capable of limiting the error due to the density variation regardless the variation
of the exponential density.

@@

Fig.~\ref{fig:sine-densities} shows the sinusoidal density functions assigned to every
spherical shell and Fig.~\ref{fig:delta-sine} shows the resulting relative differences
between the analytical and the numerical solutions.
In order to improve the visualization of the results, each curve corresponds to the
maximum difference between all shell models for the same value of $b$.

@@

>>>>

Fig.~\ref{fig:exp-densities} shows the density functions for each value of $b$ and
Fig.~\ref{fig:delta-exponential} shows the resulting relative
differences ($V$ and $g_z$).
In order to improve the visualization of the results, each curve corresponds to the
maximum difference between all shell models for the same value of $b$.
The relative difference for $V$ and $g_z$ falls below the 0.1\% threshold
for each computation grid, shell model and $b$ value if $\delta = 0.1$.
This results imply that a value of $\delta=0.1$ is needed in order to
achieve the 0.1\% accuracy threshold for both the potential and the $g_{z}$, every
shell model, computation grid and value of $b$, in case of exponential density.
These results also show that there is no significant relation between the $b$
value and the numerical error, proving that the density-based discretization algorithm
is capable of limiting the error due to the density variation regardless the variation
of the exponential density.

@@

@@

Fig.~\ref{fig:sine-densities} shows the sinusoidal density functions assigned to every
spherical shell and Fig.~\ref{fig:delta-sine} shows the resulting relative differences
between the analytical and the numerical solutions.
In order to improve the visualization of the results, each curve corresponds to the
maximum difference between all shell models for the same value of $b$.
For this kind of sinusoidal density, a value of $\delta=0.01$ is needed in order to
achieve the 0.1\% accuracy threshold for both the potential and the $g_{z}$, every
shell model, computation grid and value of $b$.
This results also proof that even for a continuous density function with several local
maximum and minimums and inflection points, the density-based discretization algorithm
performs well on computing the gravitational fields that a tesseroid with such density
generates.
